Parallel multi-objective optimization using co-evolutionary islands and search space overlapping

### 2016-12-13 hpmoon-coor.tex
Explain some stuff about migration. Closes #11

\begin{keyword}
Multi-objective algorithms \sep NSGA-II \sep Island model \sep distributed evolutionary algorithms \sep coevolution
\end{keyword}

@@

The ECJ framework \citep{ECJ} has been used to run the
experiments. Specific operators have been developed as new modules for
ECJ, and they can be downloaded from our GitHub repository under a
LGPL V3 License
\footnote{\url{https://github.com/hpmoon/hpmoon-islands}}. 
%\footnote{\url{https://ANONYMOUS-REPOSITORY}}. 
The
island model has been executed synchronously, using the ECJ Internal
Island Model, in a CentOS 5.4 machine with Intel(R) Xeon(R) CPU E5520
@2.27GHz, 16 GB RAM and Java Version 1.6.0\_16.

@@

%DESCRIPTION OF THE RESULTS
Results show that there is a difference in performance when using 512 or 2048 dimensions. Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than the obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply these methods. This contradicts the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained better results than the baseline in both dimension lengths. This can be explained because the added migration latency between nodes requires more time than the time saved during the crossover and migration.

>>>>

\begin{keyword}
Multi-objective algorithms \sep coevolution \sep NSGA-II  \sep distributed evolutionary algorithms \sep Island model
\end{keyword}

@@

The ECJ framework \citep{ECJ} has been used to run the
experiments. Specific operators have been developed as new modules for
ECJ, and they can be downloaded from our GitHub repository under a
LGPL V3 License
\footnote{\url{https://github.com/hpmoon/hpmoon-islands}}. 
%\footnote{\url{https://ANONYMOUS-REPOSITORY}}. 
The
island model has been executed asynchronously, using the ECJ distributed inter-population exchange
 model, in a cluster of 16 nodes, each one with 16 Intel(R) Xeon(R) CPU E5520
@2.27GHz processors, 16 GB RAM, Broadcom NetXtreme II BCM5716 1000Base-T (C0) PCI Express network cards, CentOS 6.8 and Java Version 1.8.0\_80. Islands have been first distributed among the nodes. That means that, for example, the run of 8 islands requires 8 different nodes, instead of the usage of the 8 processors of a single node.

@@

%DESCRIPTION OF THE RESULTS
Results show that there is a difference in performance when using 512 or 2048 dimensions. Although in some cases the overlapped methods obtain quality metrics values better or significantly equal than the obtained by the baseline, it is clear that 512 dimensions is not a value high enough to apply these methods. This contradicts the results obtained in our previous work in a shared-memory mono-processor version \citep{Garcia16hpmoon}, where the overlapping method obtained better results than the baseline in both dimension lengths. This can be explained because the added migration latency between nodes of the cluster requires more time than the time saved during the crossover and migration. This was not a problem in the mono-processor version, where the individuals shared the same memory space.
